Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-02-06 Tex/Old text/chapters/chapter02.tex
thesis update
revised Chapter 2

@@

In order to address different aspects of a project system and system's design, many public domain and commercial software are available for the solar PV market. According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization). Some tools also provide support to rebate program applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.

Manufacturers and integrators also have their own proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback of just including their own products among the possibilities of choice. In this study, the most widely used tools are presented:

@@

According to \cite{Freeman} and \cite{NRELDobos}, this is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs. According to \cite{NRELDobos}, using the calculator, requires information about the system's location, basic design parameters, and system economics. PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity's monetary value. This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin film photovoltaic modules. The production estimates that PVWatts computation does not account for many factors that are important in the design of a photovoltaic system, which makes it necessary to have the support of an energy expert. The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over a period of one year. To represent the system's physical characteristics, PVWatts requires values for six inputs: system DC size; module type; array type; system losses; array tilt angle; array azimuth angle.

@@

SAM or System Advisor Model is a software solution produced by the U.S. Department of Energy and National Renewable Energy Laboratory. According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications. SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: project managers and engineers; financial and policy analysts; technology developers; and researchers. SAM makes performance predictions and energy cost estimates for grid-connected power projects based on installation and operating costs and system design parameters that user specifies as inputs to the model. Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates, or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement. SAM is an electrical power generation model and assumes that the renewable energy system delivers power either to an electric grid, or to a grid-connected building or facility to meet the electric load. It does not model thermal energy systems that meet a thermal process load. As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems, and does not model systems with electricity storage batteries.

@@

As defined in \cite{HOMER}, this is actually a set of two tools: HOMER Legacy and HOMER Pro. HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources. HOMER Legacy is the original HOMER software version created at the National Renewable Energy Laboratory (NREL). HOMER Legacy is a free computer model that simplifies the task of evaluating design options for both off-grid and grid-connected power systems for remote, stand-alone, and distributed generation applications. HOMER's optimization and sensitivity analysis algorithms allow the user to evaluate the economic and technical feasibility of a large number of technology options. Since 2016 Homer Legacy can be found at the HOMER web site, but it is only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has no support available. For a short-time only the commercial version will remain.

The commercial version (paid), known as HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases. HOMER Pro puts together three tools in one product: optimization, simulation, and sensitivity analysis. It provides the detailed rigor of chronological simulation and optimization in a model that is intended to be easy to use and is adaptable to a wide variety of projects. For a village or community-scale power system, HOMER can model both the technical and economic factors involved in the project. For larger systems, HOMER can provide an overview that compares the cost and feasibility of different configurations. Chronological simulation is essential for modeling variable resources, such as solar and wind power and for combined heat and power applications, where the thermal load is variable. HOMER's sensitivity analysis helps determine the potential impact of uncertain factors such as fuel prices or wind speed on a given system.

@@

As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.

@@

\begin{itemize}
\item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
\item RETScreen Software Suite, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
\item And the current (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform. This version is only Windows-based and has a complete paid version, via annual subscription way.
\end{itemize}

As described by \cite{Pradhan}, RETScreen performs a standard five-step analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis. It is developed and maintained by the Government of Canada, through the CanmetENERGY Varennes Research Centre of Natural Resources; in collaboration with: NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF). RETScreen is available in 36 languages; it is a multi-awarded tool, and includes equipment databases for components manufactured and available worldwide.

@@

The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool that executes detailed long-term performance and economic analysis on a wide variety of hybrid power systems. Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system. Variations in wind speed and in load within each time step are factored into the performance predictions. The code does not consider short-term system fluctuations caused by system dynamics or component transients. This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, which is a limitation.

Table \ref{table:softwares} summarizes the tools described in this paper.  Where just Hybrid2 is mentioned, no technical support is available; only HOMER, RETScreen and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; only HOMER and RETScreen are complete, including economic analysis and even optimization-sensitive analysis. However, only the paid version of these software packages have all the features, and they run only on Windows-based operating systems.

@@

Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER remains for comparison. All tools need some parameters inherently from the manufacturer's catalog, so the project starts with manufacturer's and integrator's tool to define the basic items of the project: panels, inverters, controllers, and batteries. The potential solution is then analyzed by another tool to validate or even optimize the solution. The challenge of this study therefore is to prove that it is possible to use automated verification to validate an off-grid PV solution.

@@

The main purpose of this section is to describe the models for the elements of a stand-alone PV system: the PV generator, battery, controller, inverter, and load. The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}. The modular structure facilitates the modeling of the other system structures and the replacement of elements such as a DC load instead of an AC load.

@@

The basic element of a PV System is the PV cell, also called a Solar Cell. A PV / Solar Cell is a semiconductor device that can convert solar energy into DC electricity. The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun). When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}. If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).

To increase their application usage, a number of individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or Module). For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series. In addition, to achieve the desired voltage and current, modules are wired in series (strings) and parallel into what is called a PV array, as shown in Fig.\ref{fig:celmodarray}. The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.

@@

The growing demand for photovoltaics technologies has led to research into the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}; \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}. Modeling PV modules is one of the major components responsible for proper functioning of PV systems. However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage. Therefore, the choice of the model is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.

@@

The performance of photovoltaic systems (solar cell/panels), that is, the output current/voltage curve ($I-V$ curve), is usually studied using an equivalent circuit model. This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}. Based on these electronic components, four basic configurations are usually used when studying PV systems, as shown in Fig. \ref{fig:equivckt}.

@@

\begin{equation}
\label{eq:1diodemodel}
I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right) -1 \right] 
\end{equation}

Where:
\begin{itemize}
\item $I_{ph}$ is the photocurrent delivered by the constant current source. $I_{ph}$ is usually approximated to the reference short-circuit current of the PV panel ($I_{sc}$); 
\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed;
	\begin{itemize}
	\item $ N=1 $ in a single cell configuration. 	
	\end{itemize}	  
\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; 
	\begin{itemize}
	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
	\end{itemize}
\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
	\begin{itemize}
	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); 
	\item $ T $ is the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
	\item $ q $ is the absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
	\end{itemize}	 
\end{itemize}

@@

\begin{equation}
\label{eq:1d1rmodel}
I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] 
\end{equation}

Where $R_{s}$ is the series resistor.

@@

\begin{equation}
\label{eq:1d2rmodel}
I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
\end{equation}

Where $R_{sh}$ is the shunt resistor.

@@

For this reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters, proceeding along three different paths. The analytical methods give exact solutions by means of algebraic equations, as done by \cite{Cubas} and \cite{Brano}. However, due to the implicit nature and nonlinearity of PV cell or module characteristics, it is hard to discover the analytical solution of all unknown parameters, as described in \cite{Hasan}. Thus, numerical methods such as the Newton-Raphson method or the Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}. This happens because numerical methods give approximate solutions to the nonlinear problems without searching for exact solutions. However, numerical methods are time consuming and need long term time series data, which may not be available in developing countries. Reference~\cite{Jakhrani} used mixed methodology bringing analytical and numerical steps together.  \cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation. And \cite{Tian} used a mix of analytical and experimental methodology to establish the unknown parameters, but samples of the PV modules are necessary to perform some tests, when we use the experimental technique.

Therefore, a wide variety of models exists for estimation of the power output of PV modules (and $I-V$ or $P-V$ curves). However, this study will rely on the simplified 1-diode model, that was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% for the selected PV panels tested. In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation.

@@

As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system. An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.

With that in mind, it is important to mention that even if formal verification or a simulation shows that a PV system fails, this  does not mean that the sizing is wrong. It is important to evaluate how critical the load application is and the evaluation period. However, this analysis can be useful, for example, to improve sized battery autonomy.

@@

The mathematical model presented in section~\ref{sec:model} is important for project validation; however if an approach is used to perform the sizing of stand-alone PV systems, then the tool proposed in this thesis can perform system validation (the intended behavior), and moreover obtain optimal project sizing.

The sizing check stage can ensure that the system meets the standard project steps related 
to the critical period method for solar energy system sizing~\cite{Pinho} and adopting a MPPT (Maximum Power Point Tracking) charge controller,
which is the most common in use. Firstly, we need to correct the daily energy consumption estimated for the load 
($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), 
controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows

@@

In one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$. In other hand, the arrangement, if in series or parallel connections, it will depends on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as shown in Eq.~\eqref{eq:Icmin} and 
\eqref{eq:Vcmin}.

@@

\noindent where $Autonomy$ is a number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries.

@@

The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}. In addition, the final sizing check is performed by Equation \ref{eq:numberofc}, which validates the number of controllers adopted.

@@

The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.

@@

Moreover, it is important to verify the compatibility between charge controller and inverter, because there are some models that are not compatible with equipment from other manufacturers. Moreover, it is important to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side. Then the controller can be overcharged during this operation and to burn.

@@

During the PV system design, one of the most important aspects in ensuring power system reliability is to analyze power supply availability~\cite{Alsadi2018}. The reason is that solar energy production is intermittent and, therefore, the energy generated will usually not match the load demand. Reliable power is a generation system that has sufficient power to feed load demand in a period.

There are different methods of expressing system reliability, where the most popular ones 
are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}. In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one) the load will never be fulfilled.

LOLP is the probability for the case when load demand exceeds the power generation of the PV system. On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span. On the other, LPSP is defined as the probability of the system generating insufficient power to satisfy the load demand. The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing in system performance. However, data is not always available and dynamic analysis is complex; and this is a drawback of both LOLP and LPSP~\cite{Alsadi2018}.

Various methods of economic analysis are available. Their main objective is to determine whether the project is an acceptable investment. The usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability at the lowest cost~\cite{Alsadi2018}. The most commonly used methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.

The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime. The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}. IRR is used to evaluate the attractiveness of a project or investment.

@@

The intuitive method is simple, easily implemented, and can be used to give a rough suggestion for the preliminary design. The sizing rules are based on the designer's experience, using lowest performance data for a time period or by directly using average value (daily, monthly, or annual) of solar irradiance. This method does not consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.

in the numerical method, the design is simulated for each time step within a period. Battery state of charge is calculated and investigated. Although very accurate, it is also complex, demanding more calculation time~\cite{Park2004}.

Analytical methods are used to obtain a close relation or correlation in the form of an equation between capacities and reliabilities. The sizing task becomes much simpler than in the numerical technique; however, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.

>>>>

In this Thesis, CPAchecker will be configurated as bounded model checker.

@@

In order to address different aspects of a project system and system's design, many commercial tools are available for the solar PV market. According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation to site survey and system design tools, to sophisticated financial analysis software (with optimization). Some tools also provide support to rebate program applications and tax incentives (specific to each country or region). In contrast, other programs and worksheets focus on the technical aspects of system sizing and design.

Manufacturers and integrators also have their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback of just including their products among the possibilities of choice. In this study, the most widely used tools are presented:

@@

According to \cite{Freeman} and \cite{NRELDobos}, this is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs. According to \cite{NRELDobos}, using the calculator requires information about the system's location, basic design parameters, and system economics. PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity's monetary value. This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin-film photovoltaic modules. The production estimates that PVWatts computation does not account for many factors that are important in the design of a photovoltaic system, which makes it necessary to have the support of an energy expert. The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over one year. To represent the system's physical characteristics, PVWatts requires values for six inputs: system DC size, module type, array type, system losses, array tilt angle, and array azimuth angle.

@@

SAM or System Advisor Model is a software solution produced by the U.S. Department of Energy and National Renewable Energy Laboratory. According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications. SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: project managers and engineers; financial and policy analysts; technology developers; and researchers. SAM makes performance predictions and energy cost estimates for grid-connected power projects based on installation and operating costs and system design parameters that the user specifies as inputs to the model. Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement. SAM is an electrical power generation model and assumes that the renewable energy system delivers power either to an electric grid or to a grid-connected building or facility to meet the electric load. It does not model thermal energy systems that meet a thermal process load. As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems and does not model systems with electricity storage batteries.

@@

As defined in \cite{HOMER}, this is a set of two tools: HOMER Legacy and HOMER Pro. HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources. HOMER Legacy is the original HOMER software version created at the National Renewable Energy Laboratory (NREL). HOMER Legacy is a free computer model that simplifies the task of evaluating design options for both off-grid and grid-connected power systems for remote, stand-alone, and distributed generation applications. HOMER's optimization and sensitivity analysis algorithms allow the user to evaluate the economic and technical feasibility of a large number of technology options. Since 2016 Homer Legacy can be found at the HOMER web site, but it is only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has no support available. For a short time, only the commercial version will remain.

The commercial version (paid), known as HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing the microgrid design in all sectors, from village power and island utilities to grid-connected campuses and military bases. HOMER Pro puts together three tools in one product: optimization, simulation, and sensitivity analysis. It provides the full rigor of historical simulation and optimization in a model that is intended to be easy to use and is adaptable to a wide variety of projects. For a village or community-scale power system, HOMER can model both the technical and economic factors involved in the project. For larger systems, HOMER can provide an overview that compares the cost and feasibility of different configurations. Historical simulation is essential for modeling variable resources, such as solar and wind power, and for combined heat and power applications, where the thermal load is variable. HOMER's sensitivity analysis helps determine the potential impact of uncertain factors such as fuel prices or wind speed on a given system.

@@

As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision-makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.

@@

\begin{itemize}
\item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
\item RETScreen Software Suite, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
\item And the current (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform. This version is only Windows-based and has a complete paid version via an annual subscription way.
\end{itemize}

As described by \cite{Pradhan}, RETScreen performs a standard five-step analysis: setting and site conditions, energy model, cost analysis, emission analysis, financial analysis, sensitivity, and risk analysis. It is developed and maintained by the Government of Canada through the CanmetENERGY Varennes Research Centre of Natural Resources, in collaboration with NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF). RETScreen is available in 36 languages; it is a multi-awarded tool and includes equipment databases for components manufactured and available worldwide.

@@

The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool that executes detailed long-term performance and economic analysis on a wide variety of hybrid power systems. Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, insolation, and temperature. The power system is designed or selected by the user to predict the hybrid power system performance. Variations in wind speed and in load within each time step are factored into the performance predictions. The code does not consider short-term system fluctuations caused by system dynamics or component transients. This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, which is a limitation.

Table~\ref{table:softwares} summarizes the tools described in this thesis, where just Hybrid2 is mentioned, no technical support is available. Only HOMER, RETScreen, and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis. Only HOMER and RETScreen are complete, including economic analysis and even optimization-sensitive analysis. However, only the paid version of these software packages have all the features, and they run only on Windows-based operating systems.

@@

Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER remains for comparison. All tools need some parameters inherently from the manufacturer's catalog, so the project starts with the manufacturer's and integrator's tool to define the essential items of the project: panels, inverters, controllers, and batteries. The potential solution is then analyzed by another tool to validate or even optimize the solution. The challenge of this study, therefore, is to prove that it is possible to use automated verification to validate an off-grid PV solution.

@@

The primary purpose of this section is to describe the models for the elements of a stand-alone PV system: the PV generator, battery, controller, inverter, and load. The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}. The modular structure facilitates the modeling of the other system structures and the replacement of elements such as a DC load instead of an AC load.

@@

The fundamental element of a PV System is the PV cell, also called a Solar Cell. A PV / Solar Cell is a semiconductor device that can convert solar energy into DC electricity. The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun). When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}. If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).

In order to increase their application usage, many individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or Module). For instance, a 12 V Panel will have 36 cells connected in series, and a 24 V Panel will have 72 PV cells connected in series. Besides, to achieve the desired voltage and current, modules are wired in series (strings) and parallel into what is called a PV array, as shown in Fig.\ref{fig:celmodarray}. The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.

@@

The growing demand for photovoltaics technologies has led to research into the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}; \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}. Modeling PV modules is one of the major components responsible for the proper functioning of PV systems. However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage. Therefore, the choice of the model is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.

@@

The performance of photovoltaic systems (solar cells/panels), that is, the output current/voltage curve ($I-V$ curve), is usually studied using an equivalent circuit model. This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}. Based on these electronic components, four basic configurations are usually used when studying PV systems, as shown in Fig. \ref{fig:equivckt}.

@@

\begin{equation}
\label{eq:1diodemodel}
I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right) -1 \right], 
\end{equation}

\noindent where:
\begin{itemize}
\item $I_{ph}$ is the photocurrent delivered by the constant current source. $I_{ph}$ is usually approximated to the reference short-circuit current of the PV panel ($I_{sc}$); 
\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed;
	\begin{itemize}
	\item $ N=1 $ in a single cell configuration. 	
	\end{itemize}	  
\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; 
	\begin{itemize}
	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
	\end{itemize}
\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
	\begin{itemize}
	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); 
	\item $ T $ is the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
	\item $ q $ is the absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
	\end{itemize}	 
\end{itemize}

@@

\begin{equation}
\label{eq:1d1rmodel}
I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right], 
\end{equation}

\noindent where $R_{s}$ is the series resistor.

@@

\begin{equation}
\label{eq:1d2rmodel}
I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}},
\end{equation}

\noindent where $R_{sh}$ is the shunt resistor.

@@

For this reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters, proceeding along three different paths. The analytical methods give exact solutions through algebraic equations, as done by \cite{Cubas} and \cite{Brano}. However, due to the inherent nature and nonlinearity of PV cell or module characteristics, it is hard to discover the analytical solution of all unknown parameters, as described in \cite{Hasan}. Thus, numerical methods such as the Newton-Raphson method or the Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}. This happens because numerical methods give approximate solutions to nonlinear problems without searching for exact solutions. However, numerical methods are time-consuming and need long term time series data, which may not be available in developing countries. Reference~\cite{Jakhrani} used mixed methodology, bringing analytical and numerical steps together. \cite{Shenawy} et al. create a method to discover the unknown parameters of the PV panels through experimentation. Furthermore, \cite{Tian} used a mix of analytical and experimental methodology to establish the unknown parameters. However, samples of the PV modules are necessary to perform some tests when we use the experimental technique.

Therefore, a wide variety of models exists for estimation of the power output of PV modules (and $I-V$ or $P-V$ curves). However, this study will rely on the simplified 1-diode model, which was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% for the selected PV panels tested. Besides, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation.

@@

As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system. The seasonal availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.

With that in mind, it is essential to mention that even if formal verification or a simulation shows that a PV system fails, this does not mean that the sizing is wrong. It is essential to evaluate how critical the load application is and the evaluation period. However, this analysis can be useful, for example, to improve sized battery autonomy.

@@

The mathematical model presented in Section~\ref{sec:model} is vital for project validation. However, if an approach is used to perform the sizing of stand-alone PV systems, then the tool proposed in this thesis can perform system validation (the intended behavior), and obtain optimal project sizing.

The sizing check stage can ensure that the system meets the standard project steps related to the critical period method for solar energy system sizing~\cite{Pinho} and adopting an MPPT (Maximum Power Point Tracking) charge controller,
which is the most common in use. Firstly, we need to correct the daily energy consumption estimated for the load 
($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), 
controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows

@@

On the one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$. On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as shown in Eq.~\eqref{eq:Icmin} and 
\eqref{eq:Vcmin}.

@@

\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries.

@@

The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}. Besides, the final sizing check is performed by Equation \ref{eq:numberofc}, which validates the number of controllers adopted.

@@

The inverter sizing check is performed through three equations. Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage, and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.

@@

Moreover, it is crucial to verify the compatibility between the charge controller and inverter because some models are not compatible with equipment from other manufacturers. Moreover, it is vital to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side. Then the controller can be overcharged during this operation and to burn.

@@

During the PV system design, one of the essential aspects of ensuring power system reliability is to analyze power supply availability~\cite{Alsadi2018}. The reason is that solar energy production is intermittent and, therefore, the energy generated will usually not match the load demand. Reliable power is a generation system that has sufficient power to feed load demand in a period.

There are different methods of expressing system reliability, where the most popular ones are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}. In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one), the load will never be fulfilled.

LOLP is the probability for the case when load demand exceeds the power generation of the PV system. On the one hand, we claim that we have a reliable PV system when it can generate sufficient power to fulfill the demanded load within a period. On the other hand, LPSP is defined as the probability of the system generating insufficient power to satisfy the load demand. The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing in system performance. However, data is not always available, and dynamic analysis is complex; this is a drawback of both LOLP and LPSP~\cite{Alsadi2018}.

Various methods of economic analysis are available. Their main objective is to determine whether the project is an acceptable investment. The usual way is to perform economic analysis after reliability analysis to propose a system with high reliability at the lowest cost~\cite{Alsadi2018}. The most commonly used methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.

The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime. The net present worth is found by discounting all cash inflows and outflows, including the cost of installation, replacement, and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}. IRR is used to evaluate the attractiveness of a project or investment.

@@

The intuitive method is simple, easily implemented, and can be used to give a rough suggestion for the preliminary design. The sizing rules are based on the designer's experience, using the lowest performance data for a time period or by directly using average value (daily, monthly, or annual) of solar irradiance. This method does not consider the battery's state of charge or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.

In the numerical method, the design is simulated for each time step within a period. The battery state of charge is calculated and investigated. Although very accurate, it is also complex, demanding more calculation time~\cite{Park2004}.

Analytical methods are used to obtain a close relation or correlation in the form of an equation between capacities and reliabilities. The sizing task becomes much more straightforward than in the numerical technique. However, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.
